Global code motion of congruent instructions

### 2017-04-17 paper.tex
tables

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
Benchmark       &\% change in performance & \% change in codesize \\\hline
400.perlbench	& 1.00  & 1.00 \\\hline
401.bzip2	& 1.00  & 1.00 \\\hline
403.gcc	        & 1.00  & 1.01 \\\hline
429.mcf	        & 1.03  & 1.00 \\\hline
433.milc	& 1.00  & 1.00 \\\hline
444.namd	& 1.00  & 1.01 \\\hline
445.gobmk	& 0.99  & 1.01 \\\hline
447.dealII	& 0.95  & 1.01 \\\hline
450.soplex	& 0.99  & 0.99 \\\hline
453.povray	& 0.97  & 1.00 \\\hline
456.hmmer	& 0.99  & 1.00 \\\hline
458.sjeng	& 1.02  & 1.00 \\\hline
462.libquantum	& 1.00  & 1.00 \\\hline
464.h264ref	& 1.00  & 1.00 \\\hline
470.lbm	        & 1.00  & 1.00 \\\hline
471.omnetpp	& 1.00  & 0.99 \\\hline
473.astar	& 1.00  & 1.02 \\\hline
482.sphinx3	& 0.99  & 1.00 \\\hline
483.xalancbmk	& 1.01  & 0.99 \\\hline
Geomean         & 0.997 & 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time and code size with and without code-motion on SPEC2006 at -Ofast}
  \label{tab:code-size}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
  Benchmark       &   Baseline	        &  GCM & \%Increase     \\\hline
  400.perlbench	  &   186,829,426	& 184,690,006	& 0.99 \\\hline
  401.bzip2	  &   76,337,033	& 75,942,641	& 0.99 \\\hline
  403.gcc         &   1,079,625,231	& 1,073,158,220	& 0.99 \\\hline
  429.mcf         &   78,336,298	& 77,859,513	& 0.99 \\\hline
  433.milc	  &   272,525,306	& 269,684,876	& 0.99 \\\hline
  444.namd	  &   78,354,313	& 77,875,603	& 0.99 \\\hline
  445.gobmk	  &   261,229,078	& 258,459,798	& 0.99 \\\hline
  447.dealII	  &   643,457,797	& 638,628,331	& 0.99 \\\hline
  450.soplex	  &   245,442,755	& 242,811,500	& 0.99 \\\hline
  453.povray	  &   499,034,715	& 494,785,035	& 0.99 \\\hline
  456.hmmer	  &   214,425,324	& 211,984,389	& 0.99 \\\hline
  458.sjeng	  &   89,612,524	& 88,803,166	& 0.99 \\\hline
  462.libquantum  &   84,762,158	& 84,077,905	& 0.99 \\\hline
  464.h264ref	  &   151,049,588	& 149,284,624	& 0.99 \\\hline
  470.lbm         &   71,878,726	& 71,775,405	& 1.00 \\\hline
  471.omnetpp	  &   382,661,268	& 379,123,833	& 0.99 \\\hline
  473.astar	  &   78,351,117	& 77,872,820	& 0.99 \\\hline
  482.sphinx3	  &   158,434,290	& 156,586,406	& 0.99 \\\hline
  483.xalancbmk	  &   22,485,708,759	& 22,455,060,569& 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Change in compilation time with and without code-motion on SPEC2006 at -Ofast}
  \label{tab:compile-time}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|}
      \hline
  &  \multicolumn{3}{|c|}{Hoisted by LICM} &\multicolumn{3}{|c|}{Sunk by LICM} &\multicolumn{3}{|c|}{Functions Inlined} &  \multicolumn{3}{|c|}{Functions Deleted} \\\hline
 Benchmark        & Base        & GCM	& \%  &Base     & GCM   &\%    & Base	& GCM	  &\%   & Base	& GCM	& \% \\\hline
 400.perlbench	  & 2428	& 2480	& 2.1 & 36	& 35	& -2.8 & 1562	& 1565	  & 0.2 & 232	& 234	& 0.9  \\\hline
 401.bzip2	  & 721	        & 825	& 14.4& 3	& 3	& 0.0  & 172	& 180	  & 4.7 & 32	& 33	& 3.1  \\\hline
 403.gcc	  & 8867	& 10079	& 13.7& 143	& 182	& 27.3 & 5034	& 5080	  & 0.9 & 1303	& 130	& 0.1  \\\hline
 429.mcf	  & 55	        & 51	& -7.3& 1	& 1	& 0.0  & 4	& 4	  & 0.0 & 0 	& 0	& 0.0  \\\hline
 433.milc	  & 2537	& 2795	& 10.2& 3	& 3	& 0.0  & 75	& 81	  & 8.0 & 0	& 0	& 0.0  \\\hline
 444.namd	  & 2204	& 2206	& 0.1 & 240	& 240	& 0.0  & 387	& 390	  & 0.8 & 57	& 55	& -3.5 \\\hline
 445.gobmk	  & 3090	& 3107	& 0.6 & 18	& 19	& 5.6  & 735	& 775	  & 5.4 & 230	& 234	& 1.7  \\\hline
 447.dealII	  & 59114	& 95884	& 62.2& 60	& 8	& -86.7& 100891& 100692  & -0.2& 30219	& 29966	& -0.8 \\\hline
 450.soplex	  & 4668	& 4848	& 3.9 & 18	& 17	& -5.6 & 9801	& 9784	  & -0.2& 3125	& 3112	& -0.4 \\\hline
 453.povray	  & 9533	& 9079	& -4.8& 23	& 32	& 39.1 & 5522	& 5532	  & 0.2 & 1202	& 1201	& -0.1 \\\hline
 456.hmmer	  & 3200	& 3232	& 1.0 & 3	& 8	& 166.7& 562	& 562	  & 0.0 & 103	& 101	& -1.9 \\\hline
 458.sjeng	  & 400	        & 446	& 11.5& 0	& 0	& 0.0  & 127	& 135	  & 6.3 & 18	& 18	& 0.0  \\\hline
 462.libquantum	  & 362	        & 386	& 6.6 & 0 	& 0	& 0.0  & 87	& 87	  & 0.0 & 21	& 21	& 0.0  \\\hline
 464.h264ref	  & 17075	& 17153	& 0.5 & 4	& 4	& 0.0  & 338	& 382	  & 13.0& 72	& 72	& 0.0  \\\hline
 470.lbm	  & 39	        & 39	& 0.0 & 0	& 0	& 0.0  & 13	& 13	  & 0.0 & 4	& 4	& 0.0  \\\hline
 471.omnetpp	  & 565	        & 661	& 17.0& 32	& 30	& -6.3 & 4790	& 4843	  & 1.1 & 1321	& 1316	& -0.4 \\\hline
 473.astar	  & 691	        & 754	& 9.1 & 0	& 0	& 0.0  & 359	& 363	  & 1.1 & 113	& 113	& 0.0  \\\hline
 482.sphinx3	  & 1599	& 1693	& 5.9 & 11	& 9	& -18.2& 198	& 194	  & -2.0& 53	& 53	& 0.0  \\\hline
 483.xalancbmk	  & 9997	& 11453	& 14.6& 56	& 54	& -3.6 & 69534	& 68839	  & -1.0& 29875	& 29519	& -1.2 \\\hline
    \end{tabular}
  \end{center}
  \caption{Static metrics before and after code-hoisting on SPEC2006 at -Ofast. The \% Column show percentage increase in metric w.r.t. Base. GCM improves LICM and inlining}
  \label{tab:stats}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & \% codesize uplift & \% codesize uplift\\
Benchmarks      & at -Ofast& at -Ofast & at -Os\\\hline
400.perlbench	& 1.00  & 1.00 & 1.00\\\hline
401.bzip2	& 1.00  & 1.00 & 1.00\\\hline
403.gcc	        & 1.00  & 1.01 & 1.00\\\hline
429.mcf	        & 1.03  & 1.00 & 1.00\\\hline
433.milc	& 1.00  & 1.00 & 1.00\\\hline
444.namd	& 1.00  & 1.01 & 1.00\\\hline
445.gobmk	& 0.99  & 1.01 & 1.00\\\hline
447.dealII	& 0.95  & 1.01 & 0.98\\\hline
450.soplex	& 0.99  & 0.99 & 1.00\\\hline
453.povray	& 0.97  & 1.00 & 1.00\\\hline
456.hmmer	& 0.99  & 1.00 & 1.00\\\hline
458.sjeng	& 1.02  & 1.00 & 1.00\\\hline
462.libquantum	& 1.00  & 1.00 & 1.00\\\hline
464.h264ref	& 1.00  & 1.00 & 1.00\\\hline
470.lbm	        & 1.00  & 1.00 & 1.00\\\hline
471.omnetpp	& 1.00  & 0.99 & 1.00\\\hline
473.astar	& 1.00  & 1.02 & 1.00\\\hline
482.sphinx3	& 0.99  & 1.00 & 1.00\\\hline
483.xalancbmk	& 1.01  & 0.99 & 1.00\\\hline
Geomean         & 0.997 & 1.00 & 1.00\\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time and code size with and without code-motion on SPEC2006.}
  \label{tab:code-size}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
  Benchmarks      &   Baseline	        &  GCM & \%Increase     \\\hline
  400.perlbench	  &   186,829,426	& 184,690,006	& 0.99 \\\hline
  401.bzip2	  &   76,337,033	& 75,942,641	& 0.99 \\\hline
  403.gcc         &   1,079,625,231	& 1,073,158,220	& 0.99 \\\hline
  429.mcf         &   78,336,298	& 77,859,513	& 0.99 \\\hline
  433.milc	  &   272,525,306	& 269,684,876	& 0.99 \\\hline
  444.namd	  &   78,354,313	& 77,875,603	& 0.99 \\\hline
  445.gobmk	  &   261,229,078	& 258,459,798	& 0.99 \\\hline
  447.dealII	  &   643,457,797	& 638,628,331	& 0.99 \\\hline
  450.soplex	  &   245,442,755	& 242,811,500	& 0.99 \\\hline
  453.povray	  &   499,034,715	& 494,785,035	& 0.99 \\\hline
  456.hmmer	  &   214,425,324	& 211,984,389	& 0.99 \\\hline
  458.sjeng	  &   89,612,524	& 88,803,166	& 0.99 \\\hline
  462.libquantum  &   84,762,158	& 84,077,905	& 0.99 \\\hline
  464.h264ref	  &   151,049,588	& 149,284,624	& 0.99 \\\hline
  470.lbm         &   71,878,726	& 71,775,405	& 1.00 \\\hline
  471.omnetpp	  &   382,661,268	& 379,123,833	& 0.99 \\\hline
  473.astar	  &   78,351,117	& 77,872,820	& 0.99 \\\hline
  482.sphinx3	  &   158,434,290	& 156,586,406	& 0.99 \\\hline
  483.xalancbmk	  &   22,485,708,759	& 22,455,060,569& 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Change in compilation time with and without code-motion on SPEC2006 at -Ofast}
  \label{tab:compile-time}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|}
      \hline
  &  \multicolumn{3}{|c|}{Hoisted by LICM} &\multicolumn{3}{|c|}{Sunk by LICM} &\multicolumn{3}{|c|}{Functions Inlined} &  \multicolumn{3}{|c|}{Functions Deleted} \\\hline
 Benchmarks       & Base        & GCM	& \%  &Base     & GCM   &\%    & Base	& GCM	  &\%   & Base	& GCM	& \% \\\hline
 400.perlbench	  & 2428	& 2480	& 2.1 & 36	& 35	& -2.8 & 1562	& 1565	  & 0.2 & 232	& 234	& 0.9  \\\hline
 401.bzip2	  & 721	        & 825	& 14.4& 3	& 3	& 0.0  & 172	& 180	  & 4.7 & 32	& 33	& 3.1  \\\hline
 403.gcc	  & 8867	& 10079	& 13.7& 143	& 182	& 27.3 & 5034	& 5080	  & 0.9 & 1303	& 130	& 0.1  \\\hline
 429.mcf	  & 55	        & 51	& -7.3& 1	& 1	& 0.0  & 4	& 4	  & 0.0 & 0 	& 0	& 0.0  \\\hline
 433.milc	  & 2537	& 2795	& 10.2& 3	& 3	& 0.0  & 75	& 81	  & 8.0 & 0	& 0	& 0.0  \\\hline
 444.namd	  & 2204	& 2206	& 0.1 & 240	& 240	& 0.0  & 387	& 390	  & 0.8 & 57	& 55	& -3.5 \\\hline
 445.gobmk	  & 3090	& 3107	& 0.6 & 18	& 19	& 5.6  & 735	& 775	  & 5.4 & 230	& 234	& 1.7  \\\hline
 447.dealII	  & 59114	& 95884	& 62.2& 60	& 8	& -86.7& 100891& 100692  & -0.2& 30219	& 29966	& -0.8 \\\hline
 450.soplex	  & 4668	& 4848	& 3.9 & 18	& 17	& -5.6 & 9801	& 9784	  & -0.2& 3125	& 3112	& -0.4 \\\hline
 453.povray	  & 9533	& 9079	& -4.8& 23	& 32	& 39.1 & 5522	& 5532	  & 0.2 & 1202	& 1201	& -0.1 \\\hline
 456.hmmer	  & 3200	& 3232	& 1.0 & 3	& 8	& 166.7& 562	& 562	  & 0.0 & 103	& 101	& -1.9 \\\hline
 458.sjeng	  & 400	        & 446	& 11.5& 0	& 0	& 0.0  & 127	& 135	  & 6.3 & 18	& 18	& 0.0  \\\hline
 462.libquantum	  & 362	        & 386	& 6.6 & 0 	& 0	& 0.0  & 87	& 87	  & 0.0 & 21	& 21	& 0.0  \\\hline
 464.h264ref	  & 17075	& 17153	& 0.5 & 4	& 4	& 0.0  & 338	& 382	  & 13.0& 72	& 72	& 0.0  \\\hline
 470.lbm	  & 39	        & 39	& 0.0 & 0	& 0	& 0.0  & 13	& 13	  & 0.0 & 4	& 4	& 0.0  \\\hline
 471.omnetpp	  & 565	        & 661	& 17.0& 32	& 30	& -6.3 & 4790	& 4843	  & 1.1 & 1321	& 1316	& -0.4 \\\hline
 473.astar	  & 691	        & 754	& 9.1 & 0	& 0	& 0.0  & 359	& 363	  & 1.1 & 113	& 113	& 0.0  \\\hline
 482.sphinx3	  & 1599	& 1693	& 5.9 & 11	& 9	& -18.2& 198	& 194	  & -2.0& 53	& 53	& 0.0  \\\hline
 483.xalancbmk	  & 9997	& 11453	& 14.6& 56	& 54	& -3.6 & 69534	& 68839	  & -1.0& 29875	& 29519	& -1.2 \\\hline
    \end{tabular}
  \end{center}
  \caption{Static metrics before and after code-hoisting on SPEC2006 at -Ofast. The \% Column show percentage increase in metric w.r.t. Base. GCM improves LICM and inlining}
  \label{tab:stats}
\end{table}
